Download, Compile and Link OpenBLAS Library with R

### 2021-04-14 README.Rmd
Add .travis.yml (Travis CI).

[![DOI](https://joss.theoj.org/papers/10.21105/joss.02769/status.svg)](https://doi.org/10.21105/joss.02769)
[![last](https://www.r-pkg.org/badges/last-release/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
[![total](http://cranlogs.r-pkg.org/badges/grand-total/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
[![month](https://cranlogs.r-pkg.org/badges/ropenblas)](https://CRAN.R-project.org/package=ropenblas)

>>>>

[![DOI](https://joss.theoj.org/papers/10.21105/joss.02769/status.svg)](https://doi.org/10.21105/joss.02769)
[![Travis build status](https://travis-ci.com/prdm0/ropenblas.svg?branch=master)](https://travis-ci.com/prdm0/ropenblas)
[![last](https://www.r-pkg.org/badges/last-release/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
[![total](http://cranlogs.r-pkg.org/badges/grand-total/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
[![month](https://cranlogs.r-pkg.org/badges/ropenblas)](https://CRAN.R-project.org/package=ropenblas)
